\speculake: Hiding Malware in Speculative Execution

### 2018-12-14 paper/discussion.tex
add ack section, cut to make space

\smallskip

Alternatively multiple triggers could be used make individual state changes in
the payload program, and write in data from a local, or (as described in
Section~\ref{subsec:openssl}) remote processes. For instance, triggers could be
used to shift in data or an entire program for emulation.
%For example, a payload program
%can check a series of three distinct jump patterns corresponding to three
%different triggers. If the first trigger is detected the payload shifts in a 1
%to the state; if the second is detected it shifts in a 0. If the third trigger
%is detected it discontinues listening to the three triggers and executes the
%data shifted into the state.
%This could be a direct form of \speculake using emulation and
%decryption or more traditional malicious behavior. 
Using this method a payload program can be distributed without the encrypted
data section at all, instead having the data written into the process indirectly
at run-time without ever connecting out to any other resource.

>>>>

%\smallskip

%Alternatively multiple triggers could be used make individual state changes in
%the payload program, and write in data from a local, or (as described in
%Section~\ref{subsec:openssl}) remote processes. For instance, triggers could be
%used to shift in data or an entire program for emulation.
%%For example, a payload program
%%can check a series of three distinct jump patterns corresponding to three
%%different triggers. If the first trigger is detected the payload shifts in a 1
%%to the state; if the second is detected it shifts in a 0. If the third trigger
%%is detected it discontinues listening to the three triggers and executes the
%%data shifted into the state.
%%This could be a direct form of \speculake using emulation and
%%decryption or more traditional malicious behavior. 
%Using this method a payload program can be distributed without the encrypted
%data section at all, instead having the data written into the process indirectly
%at run-time without ever connecting out to any other resource.
